The Tor Network - Strengths and Weaknesses \\ \Large Computer Security 1 - CS5460 \\ \LaTeX{}

### 2013-11-11 paper.tex
RSA

@@

\subsubsection{RSA}
%http://security.stackexchange.com/questions/8343/what-key-exchange-mechanism-should-be-used-in-tls
%https://en.wikipedia.org/wiki/Comparison_of_TLS_implementations
%https://www.ipa.go.jp/security/rfc/RFC5246-ACJA.html

RSA...
The security of the first is based on the difficulty of factoring the product of two large primes

@@

TBB - javascript and cross-scripting

@@

% http://blog.erratasec.com/2013/09/tor-is-still-dhe-1024-nsa-crackable.html
\bibitem{Graham2013}
  Robert Graham
  \emph{\LaTeX: Tor is still DHE 1024 (NSA crackable)}.
  Errata Security, 2013

>>>>

%http://security.stackexchange.com/questions/8343/what-key-exchange-mechanism-should-be-used-in-tls
%https://en.wikipedia.org/wiki/Comparison_of_TLS_implementations
%https://www.ipa.go.jp/security/rfc/RFC5246-ACJA.html
%4134 -- 0x0039 TLS_DHE_RSA - the key exchange is an ephemeral Diffie-Hellman: the server dynamically generates a DH public key and sends it to the client; the server also signs what it sends. For DHE_RSA, the server public key must be of type RSA, and its certificate must be appropriate for signatures (the Key Usage extension, if present, must include the digitalSignature flag).
%5566 -- 0xc013 TLS_ECDHE_RSA - the server sends a dynamically generated (ephemeral?) EC Diffie-Hellman key, and signs it with its own RSA key.

@@

\subsubsection{RSA}

RSA is an algorithm for public-key cryptography. Its security is based on the infeasibility of factoring the product of two large primes. RSA, like all other public-key cryptography algorithms, relies upon two keys: one public and the other private. The public key may be published and is used for encryption and for verifying digital signatures. The private key is used for decryption, the generation of digital signatures. Thus, through RSA, only the owner of the private key can decrypt incoming messages, and only they can digitally sign outbound messages. This makes RSA extremely powerful for both authenticity and privacy.

To generate the RSA keys, two distinct prime numbers of similar bit-length are chosen at random, \textit{p} and \textit{q}. \textit{n} is computed as the product of \textit{p} and \textit{q}, and it is used as the modulus for both the public and private keys. The bit-length of \textit{n} is the RSA key length. Then let φ(n)\; =\; φ(p) φ(q)\; =\; (p − 1) (q − 1)\; where φ is Euler's totient function, whcih counts the number of positive integers less than or equal to \textit{n} that are relatively prime to \textit{n}. Then \textit{e} is chosen such that \textit{e} and φ(n) are coprime. \textit{d} is also chosen such that it is the multiplicative inverse of e modulo φ(n). The RSA public key then consists of the modulus \textit{n} and the exponent \textit{e}. The private key likewise consists of \textit{n} and the exponent \textit{d}.

A message \textit{M} is encrypted by first blocks of length less than \textit{n} using an agreed-upon padding scheme. The ciphertext \textit{c} is then computed as m^e mod n, which can be calculated quickly using the method of exponentiation by squaring. The recipient (the owner of the private key) can then recover the plaintext \textit{M} by computing c^d mod n, and then reversing the padding scheme. The decryption process is often accelerated by optimizations such as the Chinese Remainder Theorem. Furthermore, to sign a message, the owner of the private key first uses an agreed-upon hash function to compute a hash value of the message, raises it to the power of \textit{d} modulo \textit{n} and then sends that in conjuction with \textit{M}. The recipient, who only has access to the public keys, then raises the signature to the power of \textit{e} modulo \textit{n} and compares the result with his hash of the message using the same hash algorithm. If the two match, then he can prove the authenticity and integrity of the message. These two capabilities make RSA an extremely powerful tool for securing authenticity, integrity, and privacy of communication between two parties.

@@

TBB - javascript and cross-scripting
Does the web server support SSL/TLS?

@@

% http://blog.erratasec.com/2013/09/tor-is-still-dhe-1024-nsa-crackable.html
% http://thehackernews.com/2013/09/NSA-can-crack-TOR-Encryptio-Snowden-files-.html
\bibitem{Graham2013}
  Robert Graham
  \emph{\LaTeX: Tor is still DHE 1024 (NSA crackable)}.
  Errata Security, 2013
